Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-07-05 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Include post-pruning and adapt computation times
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3044 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: d8fd6d55b26bad4b64fd1299cd20da584bb3318a

The computation time on a standard computer is in the order of milliseconds for
the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency model must be re-estimated for each
time of interest, independent climatological and linear models have to be
fitted for all times of interest within a single calendar year, whereas for all
times of interest only a single circular tree and a single circular forest
model is required.

@@

>>>>

The computation time on a standard computer is in the order of milliseconds for
the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency model must be re-estimated for each
time of interest, independent climatological and linear models have to be
fitted for all times of interest within a single calendar year, whereas for all
times of interest only a single circular tree and a single circular forest
model is required. In general with respect to other applications, the computation
time for the estimation of circular regression trees and forests can be reduced by
various implemented settings, such as, e.g., the use of additional CPU cores or
binning of the input data (c.f.  Section~\ref{sec:wind:models}).

@@

An alternative split variable selection strategy is provided by cost-complexity
``post-pruning'', where a large tree is first built and then pruned back based
on the predictive performance \citep{Breiman+Friedman+Stone:1984}. As discussed
in \citet{Zeileis+Hothorn+Hornik:2008}, for model-based partitioning by
employing information criteria such as AIC~(Akaike information criterion) or
BIC~(Bayes information criterion) this strategy can be built on the same
underlying loss function as pre-pruning. However,
\citet{Schlosser+Hothorn+Zeileis:2019} show that post-pruning in an unbiased
tree algorithm is usually only superior to pre-pruning when the underlying
significance tests have low power, for example, due to a large data set.
